Viscous Transport in Eroding Porous Media

### 2019-07-24 docs/transport/erosion_transport.tex
editing in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies a Hagen-Poiseuille flow.  The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right].
\end{align}
Initially, $U=1$, and then $U$ is updated at each time step so that the
pressure drop from $x=-2$ to $x=2$ remains constant.  
{\color{red}
We
measure the area occupied by bodies 
during the eroding and record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area fraction is getting smaller $U$ is getting larger.
In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies initially and the flow rate U starts from $9.86\times 10^{-5}$. 
Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when the area fraction equals 7.57\% 
which is occupied by 8 bodies.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate U increases exponentially 
with growth rate close to $\ln10^4$. }

@@

%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
  the fluid with 20 bodies. The five first snapshots are evenly spaced in time.
  The tracers are evenly spread in the $y$-direction and released at
  $x=-1$. The sixth frame is a zoom window of the fifth frames. 
Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}

{\color{red} 
Besides the channels between two bodies, there is a single channel goes
across the domain horizontally and the flow has been concentrated in
this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
12, and 6 \& 19.  We can get a better understanding of this channel from
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In the
top three frames of  Fig.~\ref{fig:Eroding20tracer}, the flow (or
tracer) first comes from three small channels between outer wall \& body
10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
one and go into the main channel between bodies 1 \& 9.  From the first
frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
is expanding faster than other channel and bodies 4 \& 12 has vanished
and body 19 is almost gone in the forth frame.  The reason of fast
expansion of this channel is the high vorticity.  In the forth frame of
Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
high on the side of bodies which form this channel so the bodies are
eroded fast on the side of this channel or have vanished completely.

Furthermore, how long the body lasts for depends on not only the size of
the body but also the location of the body.  For example, the first
three vanishing bodies are body 12 (as t=0.0256), 4 (as t=0.0278), then
17 (as t=0.0287).  Since body 4 is located in the main flow channel so
the body 4 is vanished earlier than body 17 although the initial size of
body 4 is larger than the size of body 17.  This channel will keep
expanding and the bodies around this channel will vanish earlier than
others.  After body 17, the next 8 vanished bodies with respect to time
are body 19 (as t=0.0312),  body 7 (as t=0.0325), body 20 (as t=0.0329),
body 8 (as t=0.0349), body 10 (as t=0.0353), body 3 (as t=0.0356), body
14 (as t=0.0363), then body 9 (as t=0.0376).  All of these eight bodies
were around this channel before they are gone.

@@

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the fifth frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There is a zoom windows of
the climbing tracers trajectories in the last frame of Fig.~\ref{fig:Eroding20tracer} and
they are taken from the fifth frame of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the last frame of 
Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
%\begin{figure}[H]
%\begin{center}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
%  tracers around the bodies. Since we use a Barycentric quadrature rule
 % and the fourth order Runge Kutta method, the tracers can be very close
 % to but not penetrate the bodies.}
%\end{center}
%\end{figure}
{\color{red}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies a Hagen-Poiseuille flow.  The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right].
\end{align}
Initially, $U=1$, and then $U$ is updated at each time step so that the
pressure drop from $x=-2$ to $x=2$ remains constant.  
{\color{red}
We
measure the area occupied by bodies 
during the eroding and record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area fraction is getting smaller $U$ is getting larger.
In Fig.~\ref{fig:Eroding20flowrate}, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies initially and the flow rate $U$ starts from $9.86\times 10^{-5}$. 
Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when the area fraction equals 7.57\% 
which is occupied by 8 bodies.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}(b), the flow rate $U$ increases exponentially 
with growth rate close to $\ln10^4$. }

@@

%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
%\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
  the fluid with 20 bodies. The five first snapshots are evenly spaced in time.
  The tracers are evenly spread in the $y$-direction and released at
  $x=-1$. The bottom right frame is a zoom window of the bottom middle frames. 
Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}

{\color{red} 
Besides the channels between two bodies, there is a single channel goes
across the domain horizontally and the flow has been concentrated in
this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
12, and 6 \& 19.  We can get a better understanding of this channel from
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In Fig.~\ref{fig:Eroding20tracer}, 
the flow (or tracer) first comes from three small channels between outer wall \& body
10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
one and go into the main channel between bodies 1 \& 9.  From the first
frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
is expanding faster than other channel and bodies 4 \& 12 has vanished
and body 19 is almost gone in the forth frame.  The reason of fast
expansion of this channel is the high vorticity.  In the forth frame of
Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
high on the side of bodies which form this channel so the bodies are
eroded fast on the side of this channel or have vanished completely.

Furthermore, how long the body lasts in the fluid depends on not only the size of
the body but also the location of the body.  For example, the first
three vanishing bodies are body 12 (as t=0.0256), 4 (as t=0.0278), then
17 (as t=0.0287).  Since body 4 is located in the main flow channel so
the body 4 is vanished earlier than body 17 although the initial size of
body 4 is larger than the size of body 17.  This channel will keep
expanding and the bodies around this channel will vanish earlier than
others.  After body 17, the next 8 vanished bodies with respect to time
are body 19 (as t=0.0312),  body 7 (as t=0.0325), body 20 (as t=0.0329),
body 8 (as t=0.0349), body 10 (as t=0.0353), body 3 (as t=0.0356), body
14 (as t=0.0363), then body 9 (as t=0.0376).  All of these eight bodies
were around this channel before they are gone.

@@

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the bottom middle frame of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There is a zoom windows of
the climbing tracers trajectories in the bottom right frame of Fig.~\ref{fig:Eroding20tracer} and
they are taken from the bottom middle frame of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In the bottom right frame of 
Fig.~\ref{fig:Eroding20tracer} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
%\begin{figure}[H]
%\begin{center}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
%\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
%\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
%  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
%  tracers around the bodies. Since we use a Barycentric quadrature rule
 % and the fourth order Runge Kutta method, the tracers can be very close
 % to but not penetrate the bodies.}
%\end{center}
%\end{figure}
{\color{red}
